outline!

### 2016-05-17 paper.tex
paper: updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

The primary concern of an application developer when implementing an object
interface in Ceph is deciding how native interfaces are composed into a
compound operation. These types of decisions are commonly referred to as
physical design, and can affect performance and application flexibilty.
For instance, one valid design option is to store each log position in
an object with a name using a one-to-one mapping with the log entry position.
However, as we will see in the next section this choice of a physical design
results in poor performance in most circumstances.

@@

@@

\begin{table}
\begin{tabular}{ | l | l | l | l | l |}
\hline
Map & I/O & Entry Size & Addressing & Metadata \\ \hline
\multirow{3}{*}{1:1} & KV  & Flex     & Ceph      & KV/BS \\ \cline{2-5}
                     & BS  & Flex     & Ceph/VFS  & KV/BS \\ \hline
\multirow{4}{*}{N:1} & KV  & Flex     & \multicolumn{2}{|c|}{KV/BS} \\ \cline{2-5}
                     & WR  & Fixed    & VFS       & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & KV/BS     & KV/BS \\
\hline
\end{tabular}
\caption{The high-level design space of mapping CORFU log entry storage onto
the RADOS object storage system.}
\label{tab:pd-map}
\end{table}

>>>>

The primary concern of an application developer when implementing an object
interface in Ceph is deciding how native interfaces are composed into a
compound operation. These types of decisions are commonly referred to as
physical design, and can affect performance and application flexibilty.
For instance, one valid design option is to store each log position in
an object with a name using a one-to-one mapping with the log entry position.
However, as we will see in the next section this choice of a physical design
can result in poor performance compared to other designs.

@@

We categorize the challenges of physical design into log entry management, or
metadata management.

Our strategy is simply to construct the design space, and winnow it down using
a set of targetted experiments.

We'll start by forming a baseline performance profile without any protocol
overhead.

All designs store a log entry. We can benchmark the system without any
overhead associated with indexing or metadata management.

\paragraph*{Baseline Performance}

Figure~\ref{fig:pd-map} illustrates the two primary dimensions of the physical
design space. The first dimension concerns the strategy by which a log entry
is addressed within RADOS. In a one-to-one strategy each log entry is stored
in a distinct object with a name based on the log entry position.  This is an
attractive option because it is trivial for a client to address any log entry,
and an object interface does not require any complexity associated with
multiplexing multiple entries---addressing relies on native indexing provided
by the OSDs themselves. In contrast to a 1:1 strategy, an N:1 strategy
\emph{stripes} log entries across a smaller set of objects, introducing added
complexity into both the client and object interface implementations. The
second design dimension selects the primary storage interface for log
entries, namely the key-value or bytestream interfaces, described in
Section~\ref{sec:objclass}.

These two dimensions are represented by the first two columns of
Table~\ref{tab:pd-map} which describes the entire design space, where
\emph{KV} corresponds to the key-value interface, and the bytestream interface
is represented by \emph{AP} and \emph{EX} for an append or explicit i/o
straetgy.

. Note that we
decompose the bytestream I/O interface into two sub-strategies: I/O using
explicit offsets (EX), and appends (AP).

CORFU device interface requirements in Ceph as an object interface. So far we
have

append is more attractive, all things being equal, as it supports flexible
mapping size.

@@

\begin{table}
\begin{tabular}{ | l | l | l | l | l |}
\hline
Map & I/O & Entry Size & Addressing & Metadata \\ \hline
\multirow{3}{*}{1:1} & KV  & Flex     & Ceph      & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & Ceph/VFS  & KV/BS \\ \hline
\multirow{4}{*}{N:1} & KV  & Flex     & \multicolumn{2}{|c|}{KV/BS} \\ \cline{2-5}
                     & EX  & Fixed    & VFS       & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & KV/BS     & KV/BS \\
\hline
\end{tabular}
\caption{The high-level design space of mapping CORFU log entry storage onto
the RADOS object storage system.}
\label{tab:pd-map}
\end{table}
